Visit Scotland Notebook

### 2023-06-13 draft_work.Rmd
Re-plotted Demographic Plots Based On %, Added International Models

```{r}
international_visits %>%
  group_by(year, quarter, country) %>%
  summarise(total_visits = sum(visits),
            total_spend = sum(spend)) %>% 
  ggplot(aes(x = total_visits, y = total_spend)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}
demographics_all %>% 
  ggplot(aes(x = visits, y = expenditure)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}

ips_2002_2019 %>% 
  ggplot(aes(x = visits, y = spend)) + 
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    x = "Visits (Million)",
    y = "Expenditure (£Million) \n",
    title = "Scotland: International Visits vs. Spend",
    subtitle = "2012-2019")

```

```{r}

model <- lm(formula = spend ~ visits, data = ips_2002_2019)

model2 <- lm(formula = spend ~ visits + nights, data = ips_2002_2019)

```

```{r}
summary(model)
```

```{r}
summary(model2)
```

```{r}
library(modelr)
```

```{r}

ips_2002_2019 %>%
  add_predictions(model) %>%
  add_residuals(model) %>% 
  ggplot(aes(x = visits, y = spend)) +
  geom_point() +
  geom_line(aes(y = pred), col = "red") +
  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 4.78e-06") +
  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.8876 / Residual Standard Error: 183.3")

```

```{r}
library(ggfortify)
```

```{r}
autoplot(model)
```

>>>>

```{r}
library(broom)
library(factoextra)
```

```{r}
activities %>%
  group_by(tourism_activity) %>%
  mutate(exp_per_visit = Expenditure / Visits) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(tourism_activity, mean_exp_per_visit), y = mean_exp_per_visit,
               fill = tourism_activity == "Shopping for items that you do not regularly buy"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Activity",
    y = "Mean Expenditure \n",
    title = "Mean Expenditure per Activity  2013-2019") +
  coord_flip()
  # theme(axis.text.x = element_text(angle = 45, hjust=1))
```

```{r}
activities %>% 
  mutate(is_2019 = if_else(date_code == 2019, "2019", "2013-2018")) %>% 
  group_by(tourism_activity, is_2019) %>%
  arrange(tourism_activity) %>% 
  mutate(exp_per_visit = Expenditure / Visits) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(tourism_activity, difference_exp_per_visit), y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Activity",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018 Avg.") +
  coord_flip()
```

-----------

```{r}
activities_summary <- activities %>%
  group_by(tourism_activity) %>% 
  summarise(mean_expenditure = mean(Expenditure),
            mean_visits = mean(Visits),
            exp_per_visit = mean_expenditure / mean_visits) %>% 
  arrange(desc(exp_per_visit))
```

```{r}
activities_clust <- activities %>%
  group_by(tourism_activity) %>% 
  summarise(total_expenditure = sum(Expenditure),
            total_visits = sum(Visits)) %>% 
  select(total_expenditure, total_visits)
```

```{r}
min_k <- 1
max_k <- 5

k_clusters <- tibble(k = min_k:max_k) %>% 
  mutate(kclust = map(k, ~ kmeans(activities_clust, # Create K-means cluster beteen 1-25 clusters.
                                  centers = .x,
                                  nstart = 25)),
         tidied = map(kclust, tidy), # Tidies `kclust`
         glanced = map(kclust, glance), # Uses tidied to create a glance
         augmented = map(kclust, augment, activities_summary)) # Adds labels

# Unnest `glanced` to view `tot.withinss`
clusterings <- k_clusters %>% 
  unnest(glanced)

clusterings
```

```{r}
clusterings %>% 
  ggplot(aes(x = k, y = tot.withinss)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(1, 25, 1))
```

```{r}
fviz_nbclust(activities_clust,
             kmeans,
             method = "wss", #within sum of squares
             nstart = 25)
```

```{r}
fviz_nbclust(activities_clust,
             kmeans,
             method = "silhouette",
             nstart = 25)
```

```{r}
clusterings %>% 
  unnest(augmented) %>% # Unnest augmented created in step 5.1
  filter(k == 2) %>% # Set number of clusters
  ggplot(aes(x = total_visits, y = total_expenditure, colour = .cluster)) +
  geom_point()
```

```{r}
clusterings %>% 
  unnest(augmented) %>% # Unnest augmented created in step 5.1
  filter(k == 2) %>% 
  group_by(.cluster)
```

-----------------------------------------------------------

### 2023-06-13 visit_scotland_notebook.Rmd
Re-plotted Demographic Plots Based On %, Added International Models

```{r}
library(tidyverse)
library(here)
library(modelr)
```

@@

demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))

@@

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = age, y = mean_exp_per_visit, fill = age == "45-54 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Age Group")
```

@@

age_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(age, is_2019) %>%
  arrange(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = age, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Age",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Age Group")

@@

```{r}
gender_demographics %>%
  group_by(gender) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = gender, y = mean_exp_per_visit, fill = gender == "Male"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Gender",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Gender")
```

```{r}
gender_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(gender, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = gender, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Gender",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Gender")
```

@@

```{r}
marital_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(marital_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = marital_status, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Marital Status",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Marital Status")
```

@@

```{r}
children_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(children, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = children, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Children",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Children")
```

@@

```{r}
employment_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(employment_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = employment_status, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Employment Status",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Employment Status")
```

@@

```{r}
car_demographics %>%
  group_by(access_to_car) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = access_to_car, y = mean_exp_per_visit, fill = access_to_car == "Access to car (1+)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Car Access",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Car Access")
```
```{r}
car_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(access_to_car, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = access_to_car, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Access To Car",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Access To Car")
```

@@

```{r}
social_demographics %>%
  group_by(social_grade) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = social_grade, y = mean_exp_per_visit, fill = social_grade == "AB"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Social Gradee",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Social Grade")
```

```{r}
social_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(social_grade, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = social_grade, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Social Grade",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Social Grade")
```

@@

```{r}
ips_2002_2019 %>%
  add_predictions(model) %>%
  add_residuals(model) %>% 
  ggplot(aes(x = visits, y = spend)) +
  geom_point() +
  geom_line(aes(y = pred), col = "red") +
  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 4.78e-06") +
  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.8876 / Residual Standard Error: 183.3") +
  annotate("text", x = 1800, y = 1900, label = "Standard Error: 0.08115")
```

Diagnostic Plots: Ok, not great but passable.

- R-squared: The proportion of variance explained by the predictor(s).

- p-value: Statistical significance of effect.

- Residual Standard Error: Average distance that the observed values fall from the regression line. The smaller the value, the better the regression model is able to fit the data.

- Standard error: Uncertainty around estimated coefficient.

@@

@@

### USA

>>>>

```{r}
library(tidyverse)
library(here)
library(modelr)
library(ggfortify)
```

@@

demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
activities <- read_csv(here("data/clean_data/activities_clean.csv"))

@@

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(age, mean_exp_per_visit), y = mean_exp_per_visit, fill = age == "45-54 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Age Group") +
  coord_flip()
```

@@

age_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(age, is_2019) %>%
  arrange(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(age, difference_exp_per_visit), y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Age",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))

@@

```{r}
gender_demographics %>%
  group_by(gender) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = gender, y = mean_exp_per_visit, fill = gender == "Male"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Gender",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019")
```

```{r}
gender_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(gender, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = gender, y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Gender",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

@@

```{r}
marital_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(marital_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = marital_status, y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Marital Status",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

@@

```{r}
children_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(children, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = children, y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Children",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

@@

```{r}
employment_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(employment_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(employment_status, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Employment Status",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))

@@

```{r}
car_demographics %>%
  group_by(access_to_car) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = access_to_car, y = mean_exp_per_visit, fill = access_to_car == "Access to car (1+)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Car Access",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Car Access")
```
```{r}
car_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(access_to_car, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = access_to_car, y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Access To Car",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

@@

```{r}
social_demographics %>%
  group_by(social_grade) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(social_grade, mean_exp_per_visit), y = mean_exp_per_visit, fill = social_grade == "AB"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Social Gradee",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019") +
  coord_flip()
```

```{r}
social_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(social_grade, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(social_grade, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Social Grade",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

@@

@@

#### Summary

```{r}
ips_2002_2019 %>%
  summarise(cor(spend, visits))
```

```{r}
model_ips <- lm(formula = spend ~ visits, data = ips_2002_2019)
summary(model_ips)
```

```{r}
autoplot(model_ips)
```

```{r}
ips_2002_2019 %>%
  add_predictions(model_ips) %>%
  add_residuals(model_ips) %>% 
  ggplot(aes(x = visits, y = spend)) +
  geom_point() +
  geom_line(aes(y = pred), col = "red") +
  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 2.46e-08") +
  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.864 / Residual Standard Error: 195.2") +
  labs(
    x = "Visits (Million)",
    y = "Expenditure (£Million) \n",
    title = "Scotland: International Visits vs. Spend",
    subtitle = "2002-2019")
```

#### By Country

@@

#### USA

```{r}
ips_2002_2019_usa %>%
  summarise(cor(spend, visits))
```

```{r}
model_ips_usa <- lm(formula = spend ~ visits, data = ips_2002_2019_usa)
summary(model_ips_usa)
```

Model: spend ~ visits

Interpretation: ~83% of the variation in expenditure can be explained by the number of visits.

Question: USA visits increased by 11.5789% between 2018 and 2019 to 636 Million. If this percentage increase in visits was replicated in 2020 (709.642m), what would our model predict for expenditure?

Answer: If USA visits were increased as above, the model would predict expenditure of ~£723m (Low Estimate ~£655m, High Estimate ~£791m)

As calculated below.

Step 1.
outcome = b0 + b1 * 1st Predictor

Step 2.
expenditure = b0(intercept) + b1(coefficient) * 1st Predictor

Step 3.
expenditure = b0(intercept) + b1(coefficient) * `visits`

Step 4.
expenditure = -195.9631 + 1.2953 * `709.642`

Step 5.
expenditure = 723.2287 (Low Estimate 655.3287, High Estimate 791.1287)

predict_at <- data.frame(visits = c(709.642))

# get predicted heights at those sample_weights
predict(model_ips_usa, newdata = predict_at)
```

```{r}
723.2287  + c(-67.9, 67.9)
```

```{r}
ips_2002_2019_usa %>%
  add_predictions(model_ips_usa) %>%
  add_residuals(model_ips_usa) %>% 
  ggplot(aes(x = visits, y = spend)) +
  geom_point() +
  geom_line(aes(y = pred), col = "red") +
  labs(
    x = "Visits (Million)",
    y = "Expenditure (£Million) \n",
    title = "Scotland: USA Visits vs. Spend",
    subtitle = "2002-2019")
```

```{r}
autoplot(model_ips_usa)
```
